DisCon Children 6 vs. 1 exposure trials

### 2019-05-29 analysis/02_kids_600.Rmd
add analysis for 6v1 and 600 2yo

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/600/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/600/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,36,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

@@

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

@@

#unique(data$subid)

@@

##data <- read_csv(file="../data/kids_600.data.csv")
```

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

@@

plot_dens <- data_frame(
  age = rep(c(3,4), each = 1000),
  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
)

@@

densities_df <-
  data.frame(
    age = c(rep('3', 512),
              rep('4', 512)),
    x = c(densities$dens[[1]]$x, 
          densities$dens[[2]]$x),
    y = c(densities$dens[[1]]$y,
          densities$dens[[2]]$y)
  ) %>%
  group_by(age)%>%
  mutate (
    ci_shade = ifelse( age == "3",
      ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"), ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON")))

>>>>

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/test/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/test/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,37,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

raw_data <- raw_data %>%
  filter(subid != "190402_3_d600")

@@

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  mutate(subid = ifelse(subid == "190416_4_d6v1","190416_4_d600",subid))%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

raw_data%>%
  filter(experiment !="distribution_kids_simple_within")%>%
  group_by(subid)%>%
  summarise(n())%>%
  filter(!(subid %in% unique(log$subid)))

@@

unique(data$subid)

@@

##data <- read_csv(file="../data/kids_600.data.csv")

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)
```

@@

plot_dens <- data_frame(
  age = rep(c(2,3,4), each = 1000),
  posterior = c(unlist(plot_post%>%filter(subage == "2") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
)

@@

densities_df <-
  data.frame(
    age = c(rep('2', 512),
            rep('3', 512),
              rep('4', 512)),
    x = c(densities$dens[[1]]$x, 
          densities$dens[[2]]$x,
          densities$dens[[3]]$x),
    y = c(densities$dens[[1]]$y,
          densities$dens[[2]]$y,
          densities$dens[[3]]$y)
  ) %>%
  group_by(age)%>%
  mutate (
    ci_shade = ifelse( age == "3",
                       ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"),
                       ifelse(age == "2", ifelse( x <= plot_dens_ci%>%filter(subage == "2")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "2")%>%pull(uci), "OFF", "ON"),
      ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON"))))

### 2019-05-29 analysis/02_kids_6v1.Rmd
add analysis for 6v1 and 600 2yo

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/6v1/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/6v1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,36,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

#unique(raw_data$subid)

@@

@@

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F), 
         distribution = ifelse(distribution == "c(6, 0, 0)", "6-0-0","1-0-0"))%>%
  select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)

@@

```{r}
data %>%
  group_by(subage
           #,sex
           )%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

@@

ggplot() +
  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .0)+
  geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 5/6, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(distribution,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

p2 <- p1 %>%
  group_by(distribution) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = distribution, y = correct, col = distribution), alpha = .2 ,width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = distribution),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

kbm1 <- brm(correct_target1 ~ age_num * distribution
                      (condition| subid) + (condition | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

```{r, include = F}
kbm2 <- brm(correct_target1 ~ age_num +
                      (condition| subid) + (condition | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
child_waic <- brms::WAIC(kbm1, kbm2, compare = F)

child_weights <- model_weights(kbm1, kbm2)

@@

```{r}
data_frame(
  model = c("kbm1_w_age","kbm2"),
  WAIC = c(child_waic$kbm1$estimates[3,1],child_waic$kbm2$estimates[3,1]),
  SE = c(child_waic$kbm1$estimates[3,2],child_waic$kbm2$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```

>>>>

#files <- dir("../../kids_simple_4cat/")
files <- dir("../../kids_raw_data/test/")

raw_data <- data_frame()
for (f in files) {
#  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jf <- paste("../../kids_raw_data/test/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,37,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

unique(raw_data$subid)

raw_data <- raw_data %>%
  mutate(subage = ifelse(subid == "190313_2_d6v1","4",subage))

@@

raw_data%>%
  filter(experiment =="distribution_kids_simple_within")%>%
  group_by(subid)%>%
  summarise(n())%>%
  filter(!(subid %in% unique(log$subid)))

@@

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F), 
         distribution = ifelse(distribution == "c(6, 0, 0)", "6-0-0","1-0-0"))%>%
  select(-dob, check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)

@@

```{r}
data %>%
  group_by(subage
           )%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

@@

ggplot() +
  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .0)+
  geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, distribution,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

p2 <- p1 %>%
  group_by(subage,distribution) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = distribution, y = correct, col = subage), alpha = .2 ,width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = distribution, y = mean,  ymin = ci_lower, ymax = ci_upper, col = subage),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

# Proportion correct choice by age continous

```{r}
p5 <- data %>%
  filter(phase == 'test')%>%
  group_by(distribution,age_num, subid) %>%
  summarise(correct = mean(correct_target1))

ggplot(data = p5, aes(x = age_num, y = correct, col = distribution,fill = distribution)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_ptol()+
  scale_fill_ptol()
```

@@

kbm1 <- brm(correct_target1 ~ age_num * distribution +
                      (distribution| subid) + (distribution | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num", "b_distribution6M0M0", "b_age_num:distribution6M0M0"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

```{r, include = F}
kbm2 <- brm(correct_target1 ~ age_num +
                      (distribution| subid) + (distribution | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r}
child_waic <- brms::waic(kbm1, kbm2, compare = F)

child_weights <- model_weights(kbm1, kbm2, weights = "waic")

@@

```{r}
data_frame(
  model = c("kbm1_w_condition","kbm2"),
  WAIC = c(child_waic$loo$kbm1$estimates[3,1],child_waic$loo$kbm2$estimates[3,1]),
  SE = c(child_waic$loo$kbm1$estimates[3,2],child_waic$loo$kbm2$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```
